---
title: "Summary of SQuAPP Analysis"
date: "`r format(Sys.time(), '%d %B, %Y')`"
params:
  file_name: NA
---

**Report setup**

```{r setup, include=FALSE}
require(knitr)
require(kableExtra)
knitr::opts_chunk$set(echo = FALSE)
```

```{r util_funcs, include=FALSE}
check_var = FALSE
isProtein = FALSE
isPeptide = FALSE
isTermini = FALSE
isPTM = FALSE
print.pretty_table <- function(data,caption=NULL, format="html"){
  knitr::kable(
    data,
    format=format,
    caption=caption,
    # col.names = gsub("[.]", " "),
    table.attr = "style='width:40%;'"
  ) %>% kable_styling(
    full_width = F,
    bootstrap_options = c("striped", "hover", "condensed", "responsive"),
    position = "center"
  )
}
```

```{r load_data, include=TRUE}
message("Loading configured settings to rmarkdown")
t1 <- Sys.time()
# Check if the RDS is loaded correctly or not!
tryCatch(
  expr = {
    reportParam = readRDS(file=params$file_name)
    message("Reading Rds file...")
  },
  error = function(e){
    message("There has been an error!")
    print(e)
    knitr::knit_exit()
  },
  warning = function(w){
    message("Unexpected behaviour is found!")
    print(w)
    knitr::knit_exit()
  },
  finally = {
    t2 <- Sys.time()
  }
)
elapsed <- as.character(difftime(t2, t1, units="secs")[[1]])
message(paste("Shiny variables are correctly load in",
              elapsed, "seconds.", sep=" "))
```
# Analysis Summary

## Shared Data in Analysis
In this section of the report you will find the annotated version of your data that `SQuAPP` used internally. The full data can be download in the data setup section in the prepared data boxes.

### Reference Used
The proteome fasta reference used to annotated the different data levels provided.

```{r reference_preview, include=TRUE, results="asis"}
tmp_obj <- reportParam$shared$reference

if(!is.null(tmp_obj$param)){
  print.pretty_table(
    tmp_obj$param,
    caption="Relevant parameters for the reference used.")
}else{
  cat("> No parameters have been recorded for the reference used!\n\n")
}

# Data table preview
if(!is.null(tmp_obj$table)){
  check_var <- TRUE
  print.pretty_table(
    tmp_obj$table,
    caption="Preview of reference used in the analysis")
}else{
  cat("> Error in rendering the reference table!\n\n")
}

if(check_var){
  cat("**Fasta.sequence and Gene.name has been removed from the preview but are used in the `SQuAPP` analysis.**\n\n")
}
cat("---\n\n")
```

### Metadata Used
The metadata provided is shown with the parameters used to correctly setup
in the analysis as well as few rows of content for preview.

```{r metadata_preview, include=TRUE, results="asis"}
tmp_obj <- reportParam$shared$metadata

if(!is.null(tmp_obj$param)){
  print.pretty_table(
    tmp_obj$param,
    caption="Relevant parameters for the metadata used.")
}else{
  cat("> No parameters have been recorded for the metadata used!\n\n")
}

# Data table preview
if(!is.null(tmp_obj$table)){
  print.pretty_table(
    tmp_obj$table,
    caption="Preview of metadata used in the analysis")
}else{
  cat("> Error in rendering the metadata table!\n\n")
}

cat("---\n\n")
```

```{r initialize_protein_level, include=TRUE, results="asis"}
tmp_obj <- reportParam$protein$dataSetup
# Update the isProtein variable to be used throughout protein sections
isProtein <- !is.null(tmp_obj$isRun)

# Rendering the section headers and markdown text.
if(isProtein){
  cat("## Protein Level Analysis\n\n### Prepared Data\n\n")
}else{
  cat("> Protein level data is not run with the current analysis. **Skipping protein sections in the report.**\n\n")
}

# Rendering the Parameters Table
if(isProtein){
  if(!is.null(tmp_obj$param)){
    print.pretty_table(
      tmp_obj$param,
      caption="Parameters used to setup protein data.")
  }else{
    cat("> An error occurred when saving the parameters of the data\n\n")
  }
}

# Rendering the Data Table
if(isProtein){
  if(!is.null(tmp_obj$table)){
    print.pretty_table(
      tmp_obj$table,
      caption="Preview of prepared protein data.") %>%
      scroll_box(width="100%")
  }else{
    cat("> An error occurred when rendering the prepared protein data\n\n")
  }
}
```

```{r protein_qualityCheck, include=TRUE, results="asis"}
tmp_obj <- reportParam$protein$qualityCheck

# Render the section header and specific markdown text
if(isProtein){
  if(!is.null(tmp_obj$isRun)){
    cat("### Quality Check\n\n")
  }else{
    cat("> Quality check for this level is not run on the app!\n\n")
  }
}

# Include the parameter texts to describe the plotting process
if(isProtein){
  if(!is.null(tmp_obj$param)){
    print.pretty_table(
      tmp_obj$param,
      caption="Parameters used to setup quality check plots.")
  }else{
    cat("> An error occurred when saving plotting parameters\n\n")
  }
}

# Render the distribution plot
if(isProtein){
  if(!is.null(tmp_obj$distPlot)){
    tmp_obj$distPlot
  }else{
    cat("> An error occurred when rendering the violin plot!\n\n")
  }
}

# Render the CV plot
if(isProtein){
  if(!is.null(tmp_obj$cvPlot)){
    tmp_obj$cvPlot
  }else{
    cat("> An error occurred when rendering the cv plot!\n\n")
  }
}

# Render the identification counts plot
if(isProtein){
  if(!is.null(tmp_obj$identCount)){
    tmp_obj$identCount
  }else{
    cat("> An error occurred when rendering the number of identifications plot!\n\n")
  }
}

# Render the shared identification count plot
if(isProtein){
  if(!is.null(tmp_obj$sharedCount)){
    tmp_obj$sharedCount
  }else{
    cat("> An error occurred when rendering the shared identification count plot!\n\n")
  }
}

# Render the data completeness plot
if(isProtein){
  if(!is.null(tmp_obj$completeness)){
    tmp_obj$completeness
  }else{
    cat("> An error occurred when rendering the data completeness plot!\n\n")
  }
}

# Render the data missingness plot
if(isProtein){
  if(!is.null(tmp_obj$missingCount)){
    tmp_obj$missingCount
  }else{
    cat("> An error occurred when rendering the data missingness plot!\n\n")
  }
}
```

```{r protein_dataProcessing, include=TRUE, results="asis"}
# Create a logical variable if any dataProcessing is run in the app
isProtein_dataProcess <- (
  !is.null(reportParam$protein$dataAverage$isRun) |
  !is.null(reportParam$protein$dataAverage$isRun) |
  !is.null(reportParam$protein$dataAverage$isRun) |
  !is.null(reportParam$protein$dataAverage$isRun)
)
# Render the data processing header and specific markdown text
if(isProtein){
  if(isProtein_dataProcess){
    cat("### Data Pre-processing\n\n")
  }else{
    cat("> Data preprocessing for this data level is not run. **Skipping this section in the report.**\n\n")
  }
}
```

```{r protein_dataAverage, include=TRUE, results="asis"}
tmp_obj <- reportParam$protein$dataAverage

# Render the section header and specific markdown text
if(isProtein){
  if(isProtein_dataProcess){
    if(reportParam$protein$isRepl){
      if(!is.null(tmp_obj$isRun)){
        cat("#### Averaging Replicates\n\n")
      }else{
        cat("> Data averaging is not run for this data level.\n\n")
      }
    }else{
      cat(" > Data averaging is not applicable to this data since it doesn't contain replicas.\n\n")
    }
  }
}

if(isProtein){
  if(isProtein_dataProcess){
    if(reportParam$protein$isRepl){
      if(!is.null(tmp_obj$isReplaced)){
        if(tmp_obj$isReplaced==TRUE){
          cat("**User decided to keep the averaged state for the further analysis.**\n\n")
        }else if(tmp_obj$isReplaced==FALSE){
          cat("**User decided discarded the averaged state of the data and kept the replica state for the further analysis.**\n\n")
        }else{
          cat("> An error occurred when reading is replaced info!\n\n")
        }
      }
    }
  }
}

# Render the original table
if(isProtein){
  if(reportParam$protein$isRepl){
    if(isProtein_dataProcess){
      if(!is.null(tmp_obj$org_table)){
        print.pretty_table(
          tmp_obj$org_table,
          caption="Data State: **Before averaging**") %>%
          scroll_box(width="100%")
      }else{
        cat("> An error occurred when rendering the data state **before** processing!\n\n")
      }
    }
  }
}

# Render the original distribution plot
if(isProtein){
  if(reportParam$protein$isRepl){
    if(isProtein_dataProcess){
      if(!is.null(tmp_obj$org_distPlot)){
        tmp_obj$org_distPlot
      }else{
        cat("> An error occurred when rendering the distribution plot of original state!\n\n")
      }
    }
  }
}

# Render the original table
if(isProtein){
  if(reportParam$protein$isRepl){
    if(isProtein_dataProcess){
      if(!is.null(tmp_obj$prc_table)){
        print.pretty_table(
          tmp_obj$prc_table,
          caption="Data State: **After averaging**") %>%
          scroll_box(width="100%")
      }else{
        cat("> An error occurred when rendering the data state **after** processing!\n\n")
      }
    }
  }
}

# Render the original distribution plot
if(isProtein){
  if(reportParam$protein$isRepl){
    if(isProtein_dataProcess){
      if(!is.null(tmp_obj$prc_distPlot)){
        tmp_obj$prc_distPlot
      }else{
        cat("> An error occurred when rendering the distribution plot of processed state!\n\n")
      }
    }
  }
}
```
